Analysis of split plot design using MCMCglmm

### 2020-06-12 README.Rmd
Clean up README and add data DOI

@@

This repository is our research compendium for our analysis of the effects of
alternate wetting and drying irrigation technology on rice sheath blight
disease. The compendium contains all data, code, and text associated with the
publication. The `Rmd` files in the `analysis/paper/` directory contain details
of how all the analyses reported in the paper were conducted, as well as
instructions on how to rerun the analysis to reproduce the results. The
`data/` directory in the `analysis/` directory contains all the raw data. The
`data-raw` directory contains a README.Rmd, which when knit generates the data
used in the analysis of the paper and places `.rda` files in `data/` for the
analysis.

@@

- a Rmd file and Markdown file detailing how the raw data was handled and
Area Under the Disease Progress Stairs (AUDPS) was calculated for analysis and
the .Rda files used in the analysis were generated

@@

- the manuscript as submitted (in MS Word format) and it's Rmd source file

- all the data files (in CSV file format, in the `data/` directory)

@@

Data: [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution
requested in reuse

>>>>

### Data DOI:

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3889800.svg)](https://doi.org/10.5281/zenodo.3889800)

The raw data from this project are released and publicly available from Zenodo under a [Creative Commons Attribution 4.0 International](http://creativecommons.org/licenses/by/4.0/legalcode) licence.

@@

This repository is our research compendium for our analysis of the effects of alternate wetting and drying irrigation technology on rice sheath blight disease.
The compendium contains all data, code, and text associated with the publication.
The `Rmd` files in the `analysis/paper/` directory contain details of how all the analyses reported in the paper were conducted, as well as instructions on how to rerun the analysis to reproduce the results.
The `data/` directory in the `analysis/` directory contains all the raw data.
The `data-raw` directory contains extra files to check weather for differences between seasons, that are not included in the actual analysis.

@@

- a IRRI_weather_data.R, a file used to check weather data from IRRI weather stations to ensure that there was no significant difference in weather between seasons

@@

- the manuscript as submitted (in PDF format) and it's Rmd source file

@@

Data: [CC-4.0](http://creativecommons.org/licenses/by/4.0/legalcode) attribution requested in reuse
